CRUSE to Safe Cycling in Ireland: An Open Source Methodology to Support Active Travel

### 2023-08-01 cruse-paper.qmd
Multi format outputs

---
format:
  gfm: default
  pdf: default
title: "CRUSE to Safe Cycling in Ireland: An Open Source Methodology to Support Active Travel"
# in future: pdf!
editor: 
  markdown: 
    wrap: sentence
---

## 10th Transport Research Arena, TRA 2024, Dublin, Ireland

@@

## Abstract

>>>>

---
title: "CRUSE to Safe Cycling in Ireland: An Open Source Methodology to Support Active Travel"
format: 
  html:
    output-file: index.html
  pdf:
    output-file: cruse-paper.pdf 
  gfm:
    output-file: README.md
number-sections: true
editor: 
  # render-on-save: true
  markdown: 
    wrap: sentence
---

## 10th Transport Research Arena, TRA 2024, Dublin, Ireland {-}

@@

## Abstract {-}
